%% Elements of Nested Fibrational Cosmology
%% SPEC Branch Book: Spectroscopy Branch (Prospective)
%% Status: Architecturally constituted; pre-closure — all theorem shells carry open obligations
%%
%% Status legend:
%%   [U]  Unconditional  -- proved from spine imports and prior [U] results
%%   [C]  Conditional    -- depends on explicitly declared hypotheses
%%   [D]  Definition-structural
%%   [R]  Remark only
%%   [O]  Open obligation / named failure frontier
%%   [B]  Bridge (Book VI licensed continuum surrogate)

\documentclass[12pt,oneside]{amsbook}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1.2in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{standingrule}[theorem]{Standing Rule}
\newtheorem{openobligation}[theorem]{Open Obligation}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{scholium}[theorem]{Scholium}

\newcommand{\status}[1]{\textup{[#1]}}

%% Notation
%%   R_Spec              Spectroscopy target regime
%%   O_Spec              Spectroscopy observable family = (Spec(L_Spec), R_probe, T_Spec)
%%   L_Spec              Spectroscopy operator candidate (branch-visible)
%%   R_probe             Probe-response object
%%   T_Spec              Transition ledger
%%   G_Spec              Spectral margin (resonance isolation quantity)
%%   W                   Declared response window
%%   E_Spec              Spectroscopy endpoint datum
%%   P_Op                Spectroscopy operator packet
%%   Resp(X;P)           Quotient-visible response signature

\begin{document}

\title{SPEC Branch Book\\[6pt]
 Resonance, Probe-Response, and Certified Transition Structure}
\author{Elements of Nested Fibrational Cosmology\\
 Prospective Derived Branch}
\date{}
\maketitle
\tableofcontents
\newpage

%% ---------------------------------------------------------------
\section{Purpose and Canonical Seed}\label{sec:spec-purpose}
%% ---------------------------------------------------------------

This branch asks whether spectroscopic structure can be realized as a
lawful descendant of the NFC source architecture. The aim is not to
import the standard language of frequencies, Hamiltonians, line profiles,
or transition amplitudes as primitives, but to determine when such
language is licensed as an effective encoding of certified discrete
observable structure within a declared branch regime. This posture is
mandated by Book~I's no-smuggling stance, Book~V's branch-legitimacy
law, Book~VI's continuum-interface discipline, and Book~VII's
scoped-certificate law.

The spectroscopy branch is motivated by two existing canonical
precedents. First, the YM branch already treats spectral data of the
covariant Laplacian on the screened sector as branch-specific observable
content, together with a positive spectral margin and a staged bridge
stack. Second, the GR branch already treats a response algebra
$\mathcal{R}_{\mathrm{resp}}$ as branch-specific observable content.
A spectroscopy branch unifies these two tendencies: spectral structure
plus admissible response structure.

The initial endpoint is deliberately modest: certified resonance and
transition structure on a declared observable regime. Full physical
spectroscopy --- especially matter-rich spectroscopy depending on the
SM matter sector --- is deferred until the matter obligations are
genuinely discharged.

\begin{remark}[\status{R}]\label{rem:spec-strategic-path}
\textbf{Strategic path.}
The shortest canonical route is gauge-response spectroscopy: begin from
the YM covariant-Laplacian spectral structure, add a certified
probe-response layer, prove a transition theorem, then prove a
no-hidden-loss theorem, then discharge the Book~VI continuum-frequency
bridge. This uses the strongest present precedents while avoiding
premature dependence on the still-open SM matter sector.
\end{remark}

%% ---------------------------------------------------------------
\section{Imported Spine Structure}\label{sec:spec-imports}
%% ---------------------------------------------------------------

\textbf{Imported spine results.} All certified results of Books~I--VII
are required for lawful descent, transport accounting, continuum-interface
discipline, and closure governance. In particular:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item \emph{Book~I}: observational quotient discipline; no primitive
 geometry, fields, probability spaces, or hidden naming may be assumed.
 Spectroscopic content must therefore be quotient-visible and
 admissibly testable, not imported as background physics.
 \item \emph{Book~II}: stabilized local outcomes, collar-visible
 control, and boundary capacity structure.
 \item \emph{Book~III}: persistence and transport law for certified
 observables; additive bookkeeping.
 \item \emph{Book~IV}: the universal source object $\mathbf{U}$ and
 source-descended comparison architecture.
 \item \emph{Book~V}: lawful branchhood and branch visibility; the
 constitutional law under which a spectroscopy branch is admitted.
 \item \emph{Book~VI}: continuum language licensed only as faithful
 shorthand for certified discrete structure within a declared interface
 regime; the main gate for frequencies, line widths, response kernels,
 and other spectroscopic notation.
 \item \emph{Book~VII}: scoped certificates, promotion law, named
 frontier stability, and prohibition of hidden upgrade.
\end{enumerate}

\textbf{Imported branch precedents.}
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item \emph{YM branch}: spectral data of the covariant Laplacian on
 the screened sector as certified observable content; the operator-spectral
 template for this branch.
 \item \emph{GR branch}: a response algebra $\mathcal{R}_{\mathrm{resp}}$
 as branch-specific observable content; the response-structure template.
 \item \emph{SM super-branch}: matter content and harmonization remain
 downstream burdens rather than primitive branch assumptions.
\end{enumerate}

%% ---------------------------------------------------------------
\section{Branch-Specific Arena}\label{sec:spec-arena}
%% ---------------------------------------------------------------

\subsection{Standing Rules}\label{sec:spec-standing-rules}

\begin{standingrule}[\status{D}]\label{sr:spec-no-smuggling}
No spectroscopic quantity may be treated as primitive branch data merely
because it is familiar in external physics language. Every branch-visible
spectroscopic object must be sourced through $\mathbf{U}$, the declared
descent machinery, and the spectroscopy observable family. This is a
branch-local instance of Book~I no-smuggling and Book~V branch-legitimacy
discipline.
\end{standingrule}

\begin{standingrule}[\status{D}]\label{sr:spec-quotient-visible}
A spectroscopic distinction counts only when it is quotient-visible under
admissible tests or under a lawfully certified response object descended
from such tests. Book~I's observational quotient discipline remains
controlling.
\end{standingrule}

\begin{standingrule}[\status{D}]\label{sr:spec-continuum-gate}
Frequency language, resonance language, spectral density language, and
line-shape language may appear only after a branch-local Book~VI bridge
theorem certifies that they faithfully encode certified discrete structure
within a declared continuum interface regime.
\end{standingrule}

\begin{standingrule}[\status{D}]\label{sr:spec-no-self-promotion}
A finite or bounded operator certificate may not self-promote to a
continuum spectroscopic claim. Promotion requires an explicit transfer
theorem. This is a direct Book~VII governance consequence.
\end{standingrule}

\begin{standingrule}[\status{D}]\label{sr:spec-frontier-visibility}
Named frontiers in transition structure, response realization, spectral
no-loss, or matter coupling remain visible until discharged by theorem.
Rephrasing does not discharge them.
\end{standingrule}

\subsection{Declared Target Regime}\label{sec:spec-target-regime}

\begin{definition}[\status{D}]\label{def:spec-target-regime}
\textup{(Spectroscopy Target Regime.)}
A \emph{spectroscopy target regime} is a declared branch regime
$\mathcal{R}_{\mathrm{Spec}}$ consisting of:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item a certified observable class $\mathcal{C}_{\mathrm{obs}}$,
 \item an admissible probe family $\mathcal{P}$,
 \item a declared response window $\mathcal{W}$, and
 \item a declared comparison discipline for resonance and transition claims.
\end{enumerate}
The role of $\mathcal{R}_{\mathrm{Spec}}$ is to state explicitly where
spectroscopic claims are supposed to have force.
\end{definition}

\begin{remark}[\status{R}]\label{rem:spec-response-window}
The response window $\mathcal{W}$ is not yet a continuum frequency interval.
At this stage it is only the declared regime in which certified response
comparisons are made.
\end{remark}

\subsection{Spectroscopy Observable Family}\label{sec:spec-obs-family}

\begin{definition}[\status{D}]\label{def:spec-obs-family}
\textup{(Spectroscopy Observable Family.)}
A \emph{spectroscopy observable family} on $\mathcal{R}_{\mathrm{Spec}}$
is a triple
\[
 \mathcal{O}_{\mathrm{Spec}} \;=\;
 \bigl(\mathrm{Spec}(L_{\mathrm{Spec}}),\;
 \mathcal{R}_{\mathrm{probe}},\;
 \mathcal{T}_{\mathrm{Spec}}\bigr)
\]
where:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item $\mathrm{Spec}(L_{\mathrm{Spec}})$ is certified spectral data of
 a branch-visible operator, generator, or response morphism;
 \item $\mathcal{R}_{\mathrm{probe}}$ is a certified admissible
 probe-response object;
 \item $\mathcal{T}_{\mathrm{Spec}}$ is the branch-visible transition
 ledger induced by admissible probes on the certified observable class.
\end{enumerate}
The first component is patterned on the YM branch spectral observable
family; the second is patterned on the GR response-algebra precedent.
\end{definition}

\begin{definition}[\status{D}]\label{def:spectral-response-class}
\textup{(Spectral Response Class.)}
A \emph{spectral response class} is the quotient-visible class of response
signatures recorded by $\mathcal{R}_{\mathrm{probe}}$ under admissible
probes in $\mathcal{R}_{\mathrm{Spec}}$.
\end{definition}

\begin{definition}[\status{D}]\label{def:transition-ledger}
\textup{(Transition Ledger.)}
A \emph{transition ledger} is a certified bookkeeping object assigning to
an admissible probe episode the induced change in branch-visible spectral
response, subject to quotient visibility and transport accounting.
\end{definition}

\begin{definition}[\status{D}]\label{def:spectral-margin}
\textup{(Spectral Margin.)}
The \emph{spectral margin}
\[
 G_{\mathrm{Spec}}(X)
\]
is a branch-specific nonnegative quantity measuring observable resonance
isolation, response separation, or transition distinguishability on the
declared regime. This generalizes the YM gap-margin pattern to the
spectroscopy setting without assuming in advance that spectroscopy is
exhausted by a single gap quantity.
\end{definition}

\begin{definition}[\status{D}]\label{def:spec-continuum-interface}
\textup{(Spectroscopy Continuum Interface Regime.)}
A \emph{spectroscopy continuum interface regime} is a declared Book~VI
interface regime in which continuum notation for frequency-domain or
response-domain structure is licensed as faithful shorthand for the
asymptotic behavior of the underlying certified discrete response data.
\end{definition}

\subsection{Endpoint Datum}\label{sec:spec-endpoint}

\begin{definition}[\status{D}]\label{def:spec-endpoint}
\textup{(Spectroscopy Endpoint Datum.)}
The \emph{spectroscopy endpoint datum} is the branch-visible package
\[
 E_{\mathrm{Spec}} \;=\;
 \bigl(\mathcal{C}_{\mathrm{obs}},\;
 \mathcal{O}_{\mathrm{Spec}},\;
 G_{\mathrm{Spec}},\;
 \mathcal{W}\bigr)
\]
consisting of the certified observable class, spectroscopy observable
family, spectral margin, and declared response window.
\end{definition}

\begin{definition}[\status{D}]\label{def:lawful-spec-descendant}
\textup{(Lawful Spectroscopy Descendant Claim.)}
A \emph{lawful spectroscopy descendant claim} is a claim that the endpoint
datum $E_{\mathrm{Spec}}$ is sourced through $\mathbf{U}$ and supports a
certified resonance, transition, or response statement on the declared
regime.
\end{definition}

\subsection{Current Branch Posture}\label{sec:spec-posture}

\begin{proposition}[\status{C}]\label{prop:spec-branch-candidate}
\textup{(Spectroscopy Branch Candidate.)}
\textup{[Conditional on the spectroscopy target regime, observable family,
and endpoint datum all being sourced through $\mathbf{U}$, branch-visible,
and admitting a Book~V legitimacy witness.]}
The spectroscopy program is a lawful branch candidate.
\end{proposition}

\begin{proof}
Immediate from the branch-legitimacy doctrine (Book~V) applied to the
declared spectroscopy endpoint datum. \qed
\end{proof}

\begin{remark}[\status{R}]\label{rem:spec-posture-note}
Prop.~\ref{prop:spec-branch-candidate} constitutes the branch
architecturally. It does not yet certify any transition theorem, resonance
theorem, or continuum-interface theorem.
\end{remark}

%% ---------------------------------------------------------------
\section{Admissible Probes, Response Classes, and Transition Ledgers}
\label{sec:spec-probes}
%% ---------------------------------------------------------------

\subsection{Admissible Probes}\label{sec:spec-admissible-probes}

\begin{definition}[\status{D}]\label{def:admissible-spec-probe}
\textup{(Admissible Spectroscopy Probe.)}
An \emph{admissible spectroscopy probe} is a declared admissible process
$P \in \mathcal{P}$ whose effect on the certified observable class is
branch-visible and accountable within the spine's admissible-test
discipline.
\end{definition}

\begin{standingrule}[\status{D}]\label{sr:spec-no-hidden-probe}
No probe may introduce hidden state labels, undeclared external coordinates,
or non-certified side channels. Any probe violating this rule is not
admissible for spectroscopy claims.
\end{standingrule}

\begin{definition}[\status{D}]\label{def:probe-episode}
\textup{(Probe Episode.)}
A \emph{probe episode} on an observable object $X \in \mathcal{C}_{\mathrm{obs}}$
is an ordered application of an admissible probe together with the certified
before/after response record visible in the declared response window.
\end{definition}

\begin{remark}[\status{R}]\label{rem:probe-episode-note}
A probe episode is the spectroscopy analogue of a controlled admissible
comparison, not yet a physical measurement event in the ordinary external
sense.
\end{remark}

\subsection{Probe-Response Objects}\label{sec:spec-probe-response}

\begin{definition}[\status{D}]\label{def:probe-response-object}
\textup{(Probe-Response Object.)}
A \emph{probe-response object} is a branch-visible assignment
\[
 \mathcal{R}_{\mathrm{probe}} : (X, P) \;\mapsto\; \mathsf{Resp}(X;P)
\]
from an observable object $X$ and admissible probe $P$ to a
quotient-visible response signature $\mathsf{Resp}(X;P)$, together with
its transport and defect bookkeeping.
\end{definition}

\begin{standingrule}[\status{D}]\label{sr:spec-response-invariance}
A response signature has theorem-bearing force only to the extent that it
is invariant under presentation-level differences already eliminated by the
observational quotient.
\end{standingrule}

\begin{definition}[\status{D}]\label{def:spectroscopic-equivalence}
\textup{(Spectroscopic Equivalence.)}
Two response signatures are \emph{spectroscopically equivalent} if they
determine the same quotient-visible response class under the declared
comparison discipline of $\mathcal{R}_{\mathrm{Spec}}$.
\end{definition}

\subsection{Transition Ledgers}\label{sec:spec-transition-ledgers}

\begin{definition}[\status{D}]\label{def:one-step-transition-ledger}
\textup{(One-Step Spectroscopy Transition Ledger.)}
Given a probe-response object, the \emph{one-step spectroscopy transition
ledger}
\[
 \Delta_{\mathrm{Spec}}\!\bigl(X \xrightarrow{P} X'\bigr)
\]
records the certified change from the response class of $X$ to the
response class of $X'$ under a probe episode $P$, together with any
declared transport cost or visible defect contribution.
\end{definition}

\begin{definition}[\status{D}]\label{def:multistep-transition-ledger}
\textup{(Multi-Step Transition Ledger.)}
A \emph{multi-step transition ledger} is the additive bookkeeping object
obtained by concatenating lawful one-step spectroscopy transition ledgers
along a declared probe chain.
\end{definition}

\begin{proposition}[\status{C}]\label{prop:transition-ledger-additivity}
\textup{(Transition Ledger Additivity.)}
\textup{[Conditional on probe episodes composing lawfully and response
bookkeeping being transport-accountable.]}
Multi-step transition ledgers are additive along admissible probe chains.
\end{proposition}

\begin{proof}
This is the spectroscopy-local analogue of ledger additivity and transport
accounting from Book~III. Full force depends on the branch-local
realization of probe-response data. \qed
\end{proof}

\begin{remark}[\status{R}]\label{rem:additivity-scope}
Additivity here is bookkeeping additivity, not a claim that physical
intensities or amplitudes add linearly.
\end{remark}

\subsection{First Theorem Targets}\label{sec:spec-first-thms}

\begin{theorem}[\status{C}]\label{thm:spec-probe-realization}
\textup{(Probe-Response Realization Theorem.)}
\textup{[Conditional on O-SPEC.PR: lawful probe-realization from admissible
NFC data.]}
Given a lawful spectroscopy target regime, there exists a certified
probe-response object descending from admissible NFC data.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.PR} (Def.~\ref{def:spec-closure-ledger}).
This is the first theorem that makes spectroscopy more than bare operator
spectrum; it certifies lawful measurement-like response without importing
external measurement primitives. \qed
\end{proof}

\begin{theorem}[\status{C}]\label{thm:spec-transition-certification}
\textup{(Transition Certification Theorem.)}
\textup{[Conditional on a certified probe-response object and O-SPEC.TR.]}
Admissible probe episodes determine a lawful transition ledger on the
certified observable class.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.TR}. This theorem converts ``response
exists'' into ``transition structure is branch-visible.'' \qed
\end{proof}

\begin{theorem}[\status{C}]\label{thm:spec-no-hidden-loss}
\textup{(Spectral No-Hidden-Loss Theorem.)}
\textup{[Conditional on two lawful spectroscopy realizations sharing the
same declared continuation channel, certified branch-side spectral data,
transport invariants, and visible bridge-loss ledger; and on O-SPEC.NL.]}
The two realizations determine the same theorem-visible spectral response
class up to licensed branch equivalence.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.NL}. This is the spectroscopy analogue of
the hidden-loss control pattern in the late YM development: spectral
response must not depend on undeclared dissipative channels. \qed
\end{proof}

\begin{openobligation}[\status{C}]\label{ob:spec-frontier-min}
\textup{(Current Irreducible Spectroscopy Frontiers.)}
After the gauge-response discharge pass (O-SPEC.PR through O-SPEC.END
all conditionally discharged), the remaining genuine SPEC frontiers are:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item \emph{O-SPEC.MAT}: matter coupling --- extension from
 gauge-response spectroscopy to matter-rich spectroscopy. Gated on
 SM Branch ob:SM-matter and a lawful matter-coupling theorem.
 \item \emph{Planck calibration}: the SPEC branch transition ledger
 supplies the downstream location for identifying the SI value of
 $\hbar$ via a certified spectroscopic reference process. See
 ob:SPEC-Planck-calibration (\S\ref{sec:spec-planck}).
\end{enumerate}
These are the only remaining frontiers: neither TR nor NL gate
the gauge-response endpoint, both having been discharged.
\end{openobligation}

%% ---------------------------------------------------------------
\section{Operator/Generator Packet and Spectral Classes}
\label{sec:spec-operator}
%% ---------------------------------------------------------------

\subsection{Standing Rules for Operators}\label{sec:spec-op-sr}

\begin{standingrule}[\status{D}]\label{sr:spec-op-declared}
No operator, generator, semigroup, or response morphism may be invoked in
the spectroscopy branch unless its branch-visible role has been declared
and its observable force is licensed by the spectroscopy target regime.
\end{standingrule}

\begin{standingrule}[\status{D}]\label{sr:spec-no-continuum-promotion}
Bounded finite operator certification and continuum spectroscopic
interpretation are distinct statuses. The former does not self-promote
to the latter.
\end{standingrule}

\begin{standingrule}[\status{D}]\label{sr:spec-packet-force}
A spectral packet may be cited only with the force licensed by the declared
operator-identification theorem and its dependencies.
\end{standingrule}

\subsection{Operator / Generator Identification}\label{sec:spec-op-id}

\begin{definition}[\status{D}]\label{def:spec-operator-candidate}
\textup{(Spectroscopy Operator Candidate.)}
A \emph{spectroscopy operator candidate} is a branch-visible operator,
generator, semigroup derivative, or response morphism, denoted
$L_{\mathrm{Spec}}$, declared on the certified observable class and
proposed as the carrier of theorem-visible spectral structure.
\end{definition}

\begin{definition}[\status{D}]\label{def:spec-operator-packet}
\textup{(Spectroscopy Operator Packet.)}
The \emph{spectroscopy operator packet} is the branch-local package
\[
 \mathcal{P}_{\mathrm{Op}} \;=\;
 (L_{\mathrm{Spec}},\; \mathrm{Dom}(L_{\mathrm{Spec}}),\;
 \mathrm{Inv}_{\mathrm{Spec}},\; \mathcal{B}_{\mathrm{loss}})
\]
consisting of: (1) the declared operator candidate $L_{\mathrm{Spec}}$;
(2) its declared certified domain of force; (3) the branch-visible
transport invariants $\mathrm{Inv}_{\mathrm{Spec}}$; and (4) the
declared bridge-loss ledger $\mathcal{B}_{\mathrm{loss}}$. The
bridge-loss ledger is included so that later no-hidden-loss theorems can
be stated without ambiguity.
\end{definition}

\begin{definition}[\status{D}]\label{def:operator-id-certificate}
\textup{(Operator Identification Certificate.)}
An \emph{operator identification certificate} is a theorem or certified
bridge asserting that the declared operator candidate $L_{\mathrm{Spec}}$
is the lawful carrier of the first component of the spectroscopy observable
family.
\end{definition}

\subsection{Spectral Packets}\label{sec:spec-packets}

\begin{definition}[\status{D}]\label{def:spectral-packet}
\textup{(Spectral Packet.)}
A \emph{spectral packet} is a theorem-visible finite or bounded package of
spectroscopic data extracted from the certified operator packet, consisting
of one or more branch-visible spectral classes together with their declared
margin and scope of force.
\end{definition}

\begin{definition}[\status{D}]\label{def:resonance-isolation-class}
\textup{(Resonance Isolation Class.)}
A \emph{resonance isolation class} is a quotient-visible class of
observable response signatures whose separation from other such classes is
certified by the declared spectral margin $G_{\mathrm{Spec}}$.
\end{definition}

\begin{definition}[\status{D}]\label{def:transition-accessible-packet}
\textup{(Transition-Accessible Spectral Packet.)}
A \emph{transition-accessible spectral packet} is a spectral packet
together with the subclass of admissible probes under which the packet
participates in the certified transition ledger.
\end{definition}

\begin{remark}[\status{R}]\label{rem:accessibility-note}
Not every lawful spectral packet is automatically transition-accessible.
The transition-accessibility claim is additional force and must be
separately certified.
\end{remark}

\subsection{Bounded Certification Layer}\label{sec:spec-bounded}

\begin{theorem}[\status{C}]\label{thm:bounded-spectral-packet}
\textup{(Bounded Spectral Packet Theorem.)}
\textup{[Conditional on O-SPEC.OP: operator-identification burden
discharged and declared operator packet satisfying bounded certification
conditions.]}
There exists a theorem-visible bounded spectral packet on the certified
observable class.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.OP}. This layer is intentionally weaker than
a continuum response theorem; it certifies bounded spectral structure only.
\qed
\end{proof}

\begin{proposition}[\status{C}]\label{prop:bounded-packet-stability}
\textup{(Bounded Packet Stability.)}
\textup{[Conditional on the hypotheses of Thm.~\ref{thm:bounded-spectral-packet}.]}
Bounded spectral packets are stable under lawful admissible comparison
inside the declared regime up to licensed branch equivalence.
\end{proposition}

\begin{proof}
Stability follows from quotient visibility, transport accounting, and the
declared operator packet invariants. Full force depends on the
operator-identification theorem. \qed
\end{proof}

\subsection{Generator / Semigroup Interface}\label{sec:spec-generator}

\begin{definition}[\status{D}]\label{def:generator-compatible-family}
\textup{(Generator-Compatible Response Family.)}
A \emph{generator-compatible response family} is a spectroscopy response
family for which the certified response signatures are coherent with a
declared operator candidate in the sense required to support spectral
packet extraction.
\end{definition}

\begin{theorem}[\status{C}]\label{thm:generator-compatibility}
\textup{(Generator Compatibility Theorem.)}
\textup{[Conditional on a lawful probe-response object, a lawful operator
packet, and O-SPEC.GC.]}
The response family is generator-compatible and induces
transition-accessible spectral packets.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.GC}. \qed
\end{proof}

\subsection{First Continuum-Interface Targets}\label{sec:spec-continuum-targets}

\begin{definition}[\status{D}]\label{def:continuum-frequency-surrogate}
\textup{(Continuum Frequency Surrogate.)}
A \emph{continuum frequency surrogate} is a declared Book~VI shorthand for
the asymptotic behavior of a certified family of transition-accessible
spectral packets in a spectroscopy continuum interface regime.
\end{definition}

\begin{definition}[\status{D}]\label{def:continuum-response-density-surrogate}
\textup{(Continuum Response Density Surrogate.)}
A \emph{continuum response density surrogate} is a declared Book~VI
shorthand for the asymptotic accumulation behavior of certified discrete
response classes in a spectroscopy continuum interface regime.
\end{definition}

\begin{theorem}[\status{B}]\label{thm:continuum-frequency-surrogate}
\textup{(Continuum Frequency Surrogate Theorem.)}
\textup{[Bridge: conditional on asymptotic coherence of the family of
transition-accessible spectral packets in the Book~VI sense; and on
O-SPEC.CI.]}
Continuum frequency notation is licensed as faithful shorthand on the
declared continuum interface regime.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.CI}. The theorem does not assert a physical
continuum ontology; it licenses notation only as an effective encoding of
certified discrete structure. \qed
\end{proof}

\begin{theorem}[\status{B}]\label{thm:continuum-response-density}
\textup{(Continuum Response Density Theorem.)}
\textup{[Bridge: conditional on asymptotically coherent accumulation
behavior of certified discrete response classes; and on O-SPEC.CD.]}
Response-density notation is licensed as faithful shorthand on the declared
continuum interface regime.
\end{theorem}

\begin{proof}
Open burden: \textup{O-SPEC.CD}. Same governance note as
Thm.~\ref{thm:continuum-frequency-surrogate}. \qed
\end{proof}

%% ---------------------------------------------------------------
\section{Closure Ledger, Failure Frontier, and Status}
\label{sec:spec-closure}
%% ---------------------------------------------------------------

\subsection{Spectroscopy Closure Ledger}\label{sec:spec-ledger}

\begin{definition}[\status{D}]\label{def:spec-closure-ledger}
\textup{(Spectroscopy Closure Ledger.)}
The \emph{spectroscopy closure ledger} is the ordered burden chain:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item \textbf{O-SPEC.PR} --- probe realization,
 \item \textbf{O-SPEC.OP} --- operator / generator identification,
 \item \textbf{O-SPEC.TR} --- transition certification,
 \item \textbf{O-SPEC.NL} --- no-hidden spectral loss,
 \item \textbf{O-SPEC.GC} --- generator compatibility,
 \item \textbf{O-SPEC.CI} --- continuum frequency interface,
 \item \textbf{O-SPEC.CD} --- continuum response-density interface,
 \item \textbf{O-SPEC.END} --- endpoint packaging,
 \item \textbf{O-SPEC.MAT} --- matter coupling frontier.
\end{enumerate}
Items~(1)--(8) suffice for a gauge-response spectroscopy program.
Item~(9) is needed only for matter-rich spectroscopy.
\end{definition}

\subsection{Named Open Obligations}\label{sec:spec-obligations}

\begin{openobligation}[\status{C}]\label{ob:spec-OP}
\textup{(O-SPEC.OP: Operator / Generator Identification --- Discharged.)}
See Thm.~\ref{thm:spec-OP-discharged}.
\end{openobligation}

\begin{openobligation}[\status{C}]\label{ob:spec-TR}
\textup{(O-SPEC.TR: Transition Certification --- Discharged.)}
See Thm.~\ref{thm:spec-TR-discharged}.
\end{openobligation}

\begin{openobligation}[\status{C}]\label{ob:spec-NL}
\textup{(O-SPEC.NL: no-hidden Spectral Loss --- Discharged.)}
See Thm.~\ref{thm:spec-NL-discharged}. BLC-enhanced discharge note:
no lawful spectral-loss channel exists beyond the four declared channels
(continuation, branch-side spectral data, transport invariants, bridge-loss ledger);
this is the SPEC instance of Bridge-Ledger Completeness.
\end{openobligation}

\begin{openobligation}[\status{C}]\label{ob:spec-GC}
\textup{(O-SPEC.GC: Generator Compatibility --- Discharged.)}
See Thm.~\ref{thm:spec-GC-discharged}.
\end{openobligation}

\begin{openobligation}[\status{B}]\label{ob:spec-CI}
\textup{(O-SPEC.CI: Continuum Frequency Interface --- Discharged [B].)}
See Thm.~\ref{thm:spec-CI-discharged}.
\end{openobligation}

\begin{openobligation}[\status{B}]\label{ob:spec-CD}
\textup{(O-SPEC.CD: Continuum Response-Density Interface --- Discharged [B].)}
See Thm.~\ref{thm:spec-CD-discharged}.
\end{openobligation}

\begin{openobligation}[\status{C}]\label{ob:spec-END}
\textup{(O-SPEC.END: Endpoint Packaging --- Discharged.)}
See Thm.~\ref{thm:spec-END-discharged}.
\end{openobligation}

\begin{openobligation}[\status{C}]\label{ob:spec-MAT}
\textup{(O-SPEC.MAT: Matter Coupling Frontier --- Conditionally
Discharged.)}
\textup{[Conditional on Thm.~\ref{thm:spec-MAT-coupling} and
Thm.~\ref{thm:spec-MAT-endpoint}.]}
The branch is extended from gauge-response spectroscopy to
matter-rich spectroscopy through the lawful matter coupling
(Thm.~\ref{thm:spec-MAT-coupling}) and extended endpoint
(Thm.~\ref{thm:spec-MAT-endpoint}), harmonized with the SM
super-branch through the closed O\_ID\textsuperscript{cont} gate
chain.

\textbf{Gate update (Session L+20).}  The upstream gate
O\_ID\textsuperscript{cont} is now decomposed and conditionally
discharged on the SM side (SM Branch,
\texttt{thm:SM-IDcont-decomposition},
\texttt{thm:SM-IDcont-transfer}, \texttt{thm:SM-H0-Friedrichs},
\texttt{ob:SM-IDcont-TV}), and its single finite residual, the
screening-invariance check, is itself affirmatively resolved
(\texttt{thm:SM-H0-ScreenInv-verified}, SM Branch, Session L+21).
This obligation is therefore no longer blocked by any upstream
gate or residual: it is gated only on its own in-branch
matter-coupling construction, which is now in-toolkit actionable.
\end{openobligation}

\subsection{Two-Status Reading}\label{sec:spec-two-status}

\begin{definition}[\status{D}]\label{def:bounded-near-closure}
\textup{(Bounded Near-Closure Reading.)}
The spectroscopy branch has a \emph{bounded near-closure reading} when
O-SPEC.PR, O-SPEC.OP, O-SPEC.TR, O-SPEC.NL, and O-SPEC.GC are
discharged on the declared regime, but the continuum-interface obligations
(O-SPEC.CI, O-SPEC.CD, O-SPEC.END) remain open. This reading supports
theorem-visible bounded spectral packets, resonance isolation classes, and
transition ledgers, but not yet unrestricted continuum spectroscopic
notation.
\end{definition}

\begin{definition}[\status{D}]\label{def:continuum-endpoint-reading}
\textup{(Continuum Endpoint Reading.)}
The spectroscopy branch has a \emph{continuum endpoint reading} when, in
addition to the bounded near-closure conditions,
O-SPEC.CI, O-SPEC.CD, and O-SPEC.END are discharged on a declared
continuum interface regime. This reading licenses continuum frequency and
response-density notation within the declared interface regime and with the
force explicitly carried by the relevant bridge theorems.
\end{definition}

\subsection{Gauge-Response vs.\ Matter-Rich Spectroscopy}\label{sec:spec-gr-vs-mat}

\begin{definition}[\status{D}]\label{def:gauge-response-spectroscopy}
\textup{(Gauge-Response Spectroscopy.)}
\emph{Gauge-response spectroscopy} is the spectroscopy branch restricted
to source-descended spectral and response structure that does not require
a separately certified matter sector.
\end{definition}

\begin{definition}[\status{D}]\label{def:matter-rich-spectroscopy}
\textup{(Matter-Rich Spectroscopy.)}
\emph{Matter-rich spectroscopy} is the strengthened spectroscopy branch in
which transition and response claims depend essentially on a lawful matter
coupling sector and its harmonization with the rest of the branch endpoint
data.
\end{definition}

\begin{proposition}[\status{C}]\label{prop:gauge-vs-matter-independence}
\textup{(Gauge-Response Independence of Matter Frontier.)}
Gauge-response spectroscopy may be pursued independently of O-SPEC.MAT
provided the declared endpoint claims are restricted to the gauge-response
regime. Matter-rich spectroscopy may not be claimed without discharging
O-SPEC.MAT.
\end{proposition}

\begin{proof}
Immediate from the declared branch scopes and the rule that endpoint claims
may not exceed the force licensed by their dependencies. \qed
\end{proof}

\subsection{Current Status Proposition}\label{sec:spec-current-status}

\begin{proposition}[\status{C}]\label{prop:spec-current-status}
\textup{(Spectroscopy Branch: Current Status.)}
The spectroscopy branch is a prospective lawful descendant program with
strong architectural precedent but without canonical closure. More
precisely:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item it inherits lawful descent conditions from the spine and
 branch-governance books (Books~I--VII);
 \item it inherits an operator-spectral precedent from the YM branch;
 \item it inherits a response-structure precedent from the GR branch;
 \item it does not yet possess a certified transition theorem;
 \item it does not yet possess a certified no-hidden-loss theorem for
 spectroscopy proper;
 \item it does not yet possess a fully discharged continuum spectroscopy
 bridge;
 \item full matter-rich spectroscopy remains downstream of O-SPEC.MAT.
\end{enumerate}
\end{proposition}

\begin{proof}
Items~(1)--(3) state the architectural inputs already in place.
Items~(4)--(7) are exactly the named open obligations recorded in the
closure ledger (Def.~\ref{def:spec-closure-ledger}). \qed
\end{proof}

%% ---------------------------------------------------------------
\section{Dependency Ledger}\label{sec:spec-dep-ledger}
%% ---------------------------------------------------------------

\textbf{Primary upstream dependencies.}
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item Book~I supplies quotient-visible observable distinction and blocks
 primitive spectroscopic imports.
 \item Book~II supplies stabilized local control and observable boundary
 structure needed for declared response windows.
 \item Book~III supplies transport accounting and additive bookkeeping
 needed for transition ledgers.
 \item Book~IV supplies the universal source $\mathbf{U}$ through which
 the spectroscopy endpoint must descend.
 \item Book~V supplies the branch-legitimacy law by which the
 spectroscopy branch is constituted.
 \item Book~VI supplies the conditions under which continuum frequency
 and response-density notation become lawful.
 \item Book~VII supplies scoped-certificate law, frontier stability, and
 promotion control.
\end{enumerate}

\textbf{Primary branch precedents.}
\begin{enumerate}[label=\textup{(\arabic*)}]
 \setcounter{enumi}{7}
 \item YM branch supplies the operator-spectral template.
 \item GR branch supplies the response-structure template.
 \item SM super-branch identifies the matter frontier
 (O-SPEC.MAT) as downstream rather than primitive.
\end{enumerate}

\textbf{Internal branch dependency flow.}
\begin{enumerate}[label=\textup{(\arabic*)}]
 \setcounter{enumi}{10}
 \item The target regime $\mathcal{R}_{\mathrm{Spec}}$ is prior to all
 branch-local theorem claims.
 \item The probe-response object depends on lawful descent and admissible
 probe definitions.
 \item The operator packet depends on operator identification and declared
 branch invariants.
 \item Transition ledgers depend jointly on probe-response realization
 and operator / generator compatibility.
 \item No-hidden-loss control depends on declared continuation channel,
 operator packet, transport invariants, and bridge-loss ledger.
 \item Continuum surrogates depend on certified transition-accessible
 spectral packets and Book~VI asymptotic coherence.
 \item Endpoint packaging depends on all prior certified branch-local
 components and the declared scope of force.
 \item Matter-rich spectroscopy depends additionally on O-SPEC.MAT and
 later harmonization with the SM super-branch.
\end{enumerate}


%% ---------------------------------------------------------------
\section{Obligation Discharges}\label{sec:spec-discharges}
%% ---------------------------------------------------------------

This section discharges obligations O-SPEC.PR through O-SPEC.END.
Each discharge replaces the corresponding open obligation with a
conditional theorem whose hypotheses are stated explicitly.
O-SPEC.MAT remains an open obligation, genuinely gated on SM matter
sector progress (SM Branch, \texttt{ob:SM-matter}).

\subsection{O-SPEC.PR: Probe Realization}\label{sec:spec-PR}

\begin{theorem}[\status{C}]\label{thm:spec-PR-discharged}
\textup{(Probe-Response Realization --- O-SPEC.PR Conditionally Discharged.)}
\textup{[Conditional on: (1) a declared spectroscopy target regime
$\mathcal{R}_{\mathrm{Spec}}$ with admissible probe family
$\mathcal{P} \subseteq \mathcal{T}_n$ (Book~I admissible tests) and
certified observable class $\mathcal{C}_{\mathrm{obs}}$ descended from
$\mathbf{U}$ (Book~IV, Thm.~\ref{thm:universal-completion}); and (2)
Book~II transfer structure
(Def.~\ref{def:transfer-system}) on $\mathcal{C}_{\mathrm{obs}}$.]}
There exists a certified probe-response object
\[
 \mathcal{R}_{\mathrm{probe}} : (X, P) \;\mapsto\;
 \mathsf{Resp}(X;P) \;:=\; [T_n(X)]_{\sim_n}
\]
where $T_n \in \mathcal{P}$ is the admissible test underlying probe~$P$
and $[\cdot]_{\sim_n}$ is the observable equivalence class
(Book~I, Def.~\ref{def:obs-equiv}). The assignment is quotient-visible,
transport-accountable (Book~III), and defect-tracked via the
Book~II boundary capacity structure restricted to $\mathcal{R}_{\mathrm{Spec}}$.
\end{theorem}

\begin{proof}
The observable equivalence relation $\sim_n$ (Book~I) is already defined
on all admissible-test outcomes. Restricting to the probe family
$\mathcal{P} \subseteq \mathcal{T}_n$ gives quotient-visible response
classes by the no-smuggling standing rule (Sr.~\ref{sr:spec-no-smuggling}).
Transport accounting is provided by Book~III persistence and transfer
structure. The bridge-loss ledger inherits from Book~II boundary
capacity bookkeeping. No external measurement primitives are required.
\qed
\end{proof}

\begin{remark}[\status{R}]\label{rem:spec-PR-scope}
The response assignment here is the structural minimum: it records the
observable equivalence class of test outcomes. The richer response
structure (resonance isolation, spectral packets) builds on this foundation
in subsequent discharges.
\end{remark}

\subsection{O-SPEC.OP: Operator Identification}\label{sec:spec-OP}

\begin{theorem}[\status{C}]\label{thm:spec-OP-discharged}
\textup{(Spectroscopy Operator Identification --- O-SPEC.OP Conditionally Discharged.)}
\textup{[Conditional on: O-SPEC.PR discharged
(Thm.~\ref{thm:spec-PR-discharged}); Phase-A
(Cor.~\ref{cor:phase-a-universal-K07}, Book~II, [U]); and the
declared spectroscopy target regime $\mathcal{R}_{\mathrm{Spec}}$ being
a gauge-response regime in which the covariant-Laplacian pattern of the
YM branch applies.]}
There exists a certified spectroscopy operator candidate
$L_{\mathrm{Spec}}$ on the declared observable class, namely the
restriction of the Book~III unified coercive-transport operator
(Thm.~\ref{thm:unified-coercive}) to $\mathcal{C}_{\mathrm{obs}}$,
with:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item certified domain $\mathrm{Dom}(L_{\mathrm{Spec}})$ from the
 Book~II local stabilized sector restricted to $\mathcal{R}_{\mathrm{Spec}}$;
 \item transport invariants $\mathrm{Inv}_{\mathrm{Spec}}$ inherited
 from Book~III;
 \item bridge-loss ledger $\mathcal{B}_{\mathrm{loss}}$ recording the
 collar-to-continuum control quantity from Book~VI;
 \item spectral data $\mathrm{Spec}(L_{\mathrm{Spec}})$ forming the
 first component of $\mathcal{O}_{\mathrm{Spec}}$.
\end{enumerate}
The YM covariant Laplacian $L_A$ (YM Branch) is a special case of this
identification in the screened gauge-algebra sector.
\end{theorem}

\begin{proof}
The Book~III governing theorem (Thm.~\ref{thm:governing}) constructs a
coercive-transport operator on every certified observable class that is a
persistent transport-system descendant of $\mathbf{U}$. Restricting to
$\mathcal{C}_{\mathrm{obs}}$ on $\mathcal{R}_{\mathrm{Spec}}$ gives
$L_{\mathrm{Spec}}$. The transport-compatible invariant bilinear form
(YM Branch, Def.~\ref{def:transport-compatible-bilinear}) provides the
ambient inner-product structure for $\mathrm{Spec}(L_{\mathrm{Spec}})$.
The YM precedent (Phase-A) certifies this identification in the
gauge-response setting. The operator packet is therefore fully declared.
\qed
\end{proof}

\subsection{O-SPEC.TR: Transition Certification}\label{sec:spec-TR}

\begin{theorem}[\status{C}]\label{thm:spec-TR-discharged}
\textup{(Transition Certification --- O-SPEC.TR Conditionally Discharged.)}
\textup{[Conditional on: O-SPEC.PR (Thm.~\ref{thm:spec-PR-discharged})
and O-SPEC.OP (Thm.~\ref{thm:spec-OP-discharged}) discharged; Book~III
transport-invariant observable class
(Def.~\ref{def:transport-invariant}) and ledger additivity
(Lem.~\ref{lem:transport-equiv-null}).]}
Admissible probe episodes on $\mathcal{C}_{\mathrm{obs}}$ determine a
lawful transition ledger $\mathcal{T}_{\mathrm{Spec}}$ on the certified
observable class. Concretely, the one-step ledger entry is
\[
 \Delta_{\mathrm{Spec}}\!\bigl(X \xrightarrow{P} X'\bigr)
 \;:=\; \mathsf{Resp}(X';P) \ominus \mathsf{Resp}(X;P)
\]
in the transport-difference class, where $\ominus$ denotes the
transport-accountable subtraction of observable equivalence classes.
\end{theorem}

\begin{proof}
Both $\mathsf{Resp}(X;P)$ and $\mathsf{Resp}(X';P)$ are quotient-visible
(O-SPEC.PR). Their difference $\ominus$ is well-defined in the
transport-difference class: by Lem.~\ref{lem:transport-equiv-null},
transport-equivalent inputs produce transport-equivalent difference
classes, so the assignment is invariant under admissible relabelling.
The declared response window $\mathcal{W}$ bounds the regime. The probe
$P$ is admissible (Sr.~\ref{sr:spec-no-hidden-probe}), so no-hidden
channels enter. Additivity of multi-step ledgers follows from
Prop.~\ref{prop:transition-ledger-additivity} (now fully licensed since
both inputs are certified). \qed
\end{proof}

\subsection{O-SPEC.NL: no-hidden Spectral Loss}\label{sec:spec-NL}

\begin{definition}[\status{D}]\label{def:spec-localization-package}
\textup{(SPEC Localization Package.)}
A \emph{SPEC localization package} is a tuple
$\mathcal{L}_{\mathrm{Spec}} = (C, K, T, \Lambda, g)$
where: $C$ is the declared continuation/probe channel;
$K = \mathrm{Spec}(L_{\mathrm{Spec}})$ is the certified branch-side
spectral data; $T = \mathrm{Inv}_{\mathrm{Spec}}$ is the transported
invariant; $\Lambda = \mathcal{B}_{\mathrm{loss}}$ is the visible
bridge-loss ledger; and $g$ is the theorem-visible spectral response class.
The package is lawful when every component descends from $\mathbf{U}$
and is branch-visible.
\end{definition}

\begin{theorem}[\status{C}]\label{thm:spec-BLC}
\textup{(SPEC Bridge-Ledger Completeness.)}
\textup{[Conditional on O-SPEC.TR discharged and two lawful SPEC
localization packages $\mathcal{L}_1$, $\mathcal{L}_2$ agreeing on
$(C_1=C_2,\; K_1=K_2,\; T_1=T_2,\; \Lambda_1=\Lambda_2)$.]}
Then $g_1 = g_2$ up to licensed branch equivalence.
No lawful spectral-loss channel exists beyond the four declared
components $(C, K, T, \Lambda)$.
\end{theorem}

\begin{proof}
Assume $g_1 \neq g_2$. Since $C_1=C_2$, the difference is not a
continuation difference. Since $K_1=K_2$, it is not branch-side
spectral content. Since $T_1=T_2$, it is not transport-invariant
drift. Since $\Lambda_1=\Lambda_2$, it is not ledger-visible loss.
A fifth lawful spectral-loss channel would require an undeclared
dissipative source beyond the declared four; this is ruled out by the
exhaustive source-image condition (\texttt{def:exhaustive-source-image},
Book~IV) applied to $\mathbf{U}$. Therefore $g_1 = g_2$ up to
licensed branch equivalence.
\qed
\end{proof}


\begin{theorem}[\status{C}]\label{thm:spec-NL-discharged}
\textup{(Spectral No-Hidden-Loss --- O-SPEC.NL Conditionally Discharged.)}
\textup{[Conditional on: O-SPEC.TR discharged
(Thm.~\ref{thm:spec-TR-discharged}); two lawful spectroscopy
realizations sharing the same declared continuation channel, certified
branch-side spectral data $\mathrm{Spec}(L_{\mathrm{Spec}})$, transport
invariants $\mathrm{Inv}_{\mathrm{Spec}}$, and visible bridge-loss
ledger $\mathcal{B}_{\mathrm{loss}}$; and the universal completion
theorem (Thm.~\ref{thm:universal-completion}, Book~IV, [U]).]}
The two realizations determine the same theorem-visible spectral response
class up to licensed branch equivalence.
\end{theorem}

\begin{proof}
Let $\mathcal{R}_1$ and $\mathcal{R}_2$ be two such realizations.
By O-SPEC.OP, the operator $L_{\mathrm{Spec}}$ is uniquely identified as
the restriction of the Book~III coercive-transport operator to
$\mathcal{C}_{\mathrm{obs}}$; its spectral data is therefore the same
for both realizations. By O-SPEC.TR, the transition ledger
$\Delta_{\mathrm{Spec}}$ is determined solely by the observable quotient
classes and the transport-difference construction. Since both
realizations share the same declared continuation channel, spectral data,
transport invariants, and bridge-loss ledger, their transition-ledger
entries coincide. Any discrepancy would require an undeclared dissipative
channel, which is ruled out by the source-image discipline
(Def.~\ref{def:exhaustive-source-image}, Book~IV) applied to
$\mathbf{U}$. Hence the spectral response classes agree up to the
licensed branch equivalence relation. \qed
\end{proof}

\subsection{O-SPEC.GC: Generator Compatibility}\label{sec:spec-GC}

\begin{theorem}[\status{C}]\label{thm:spec-GC-discharged}
\textup{(Generator Compatibility --- O-SPEC.GC Conditionally Discharged.)}
\textup{[Conditional on: O-SPEC.PR (Thm.~\ref{thm:spec-PR-discharged})
and O-SPEC.OP (Thm.~\ref{thm:spec-OP-discharged}) discharged; and the
declared probe family $\mathcal{P}$ being admissible in the sense that
probes exercise the spectral modes of $L_{\mathrm{Spec}}$ on
$\mathcal{C}_{\mathrm{obs}}$.]}
The probe-response object $\mathcal{R}_{\mathrm{probe}}$ is
generator-compatible with the operator packet $\mathcal{P}_{\mathrm{Op}}$,
and therefore induces transition-accessible spectral packets.
\end{theorem}

\begin{proof}
By O-SPEC.OP, $L_{\mathrm{Spec}}$ is the restriction of the Book~III
coercive-transport operator. The Book~III governing theorem
(Thm.~\ref{thm:governing}) shows that admissible tests detect precisely
those observable features stabilized by the coercive operator, because
the admissible-test class $\mathcal{T}_n$ is defined by transport
persistence under the same collar-algebra dynamics that $L_{\mathrm{Spec}}$
generates. Therefore $\mathsf{Resp}(X;P) = [T_n(X)]$ lies in the
eigenclass of $L_{\mathrm{Spec}}$ on $X$: each response class records a
quotient-visible spectral mode. Transition-accessible packets are then
those spectral packets visible to probes in $\mathcal{P}$, which by the
admissible-test design is precisely the branch-visible subset of
$\mathrm{Spec}(L_{\mathrm{Spec}})$. Generator compatibility is
established. \qed
\end{proof}

\subsection{O-SPEC.CI: Continuum Frequency Interface}\label{sec:spec-CI}

\begin{theorem}[\status{B}]\label{thm:spec-CI-discharged}
\textup{(Continuum Frequency Interface --- O-SPEC.CI Discharged.)}
\textup{[Bridge: conditional on O-SPEC.GC discharged
(Thm.~\ref{thm:spec-GC-discharged}); asymptotic coherence of the
transition-accessible spectral packet family in the Book~VI sense
(Thm.~\ref{thm:continuum-bridge-schema}, Book~VI, [U]); and a declared
spectroscopy continuum interface regime
(Def.~\ref{def:spec-continuum-interface}).]}
On the declared continuum interface regime, continuum frequency notation
$\nu = \lambda / (2\pi)$ (or analogous parameterization) is licensed as
faithful shorthand for the asymptotic behavior of the certified family of
transition-accessible spectral packets $\{\lambda_n\} = \mathrm{Spec}(L_{\mathrm{Spec}})$.
\end{theorem}

\begin{proof}
The Book~VI Continuum Bridge Schema (Thm.~\ref{thm:continuum-bridge-schema})
licenses continuum notation whenever: (i) the underlying discrete data is
certified; (ii) the continuum regime is declared; (iii) the notation
faithfully encodes the asymptotic behavior of the discrete data. By
O-SPEC.GC, the transition-accessible spectral packet family is certified.
Under the declared asymptotic coherence hypothesis, the eigenvalue sequence
$\lambda_n$ satisfies the Book~VI increment-control condition. The frequency
surrogates $\nu_n = \lambda_n / (2\pi)$ then faithfully encode $\lambda_n$
as an effective continuum parameterization within the declared interface
regime. No continuum ontology is asserted; the notation is shorthand only.
\qed
\end{proof}

\subsection{O-SPEC.CD: Continuum Response-Density Interface}\label{sec:spec-CD}

\begin{theorem}[\status{B}]\label{thm:spec-CD-discharged}
\textup{(Continuum Response-Density Interface --- O-SPEC.CD Discharged.)}
\textup{[Bridge: conditional on O-SPEC.CI discharged
(Thm.~\ref{thm:spec-CI-discharged}); and the certified discrete response
classes admitting asymptotically coherent accumulation behavior in the
Book~VI sense on the declared spectroscopy continuum interface regime.]}
Response-density notation $\rho(\nu)\,\mathrm{d}\nu$ is licensed as
faithful shorthand for the asymptotic accumulation behavior of the certified
discrete spectral response classes on the declared continuum interface
regime.
\end{theorem}

\begin{proof}
By O-SPEC.CI, the continuum frequency parameterization is licensed.
The Book~VI Continuum Bridge Schema applies a second time: the discrete
response classes $\{\mathsf{Resp}(X_n; P)\}$ accumulate in the
continuum-interface regime according to the asymptotic coherence
hypothesis. The response-density notation $\rho(\nu)\,\mathrm{d}\nu$
is the faithful encoding of this accumulation, with no additional continuum
structure assumed. Both CI and CD use the same Book~VI bridge theorem;
CD is the accumulation-density instance of the same schema. \qed
\end{proof}

\subsection{O-SPEC.END: Endpoint Packaging}\label{sec:spec-END}

\begin{theorem}[\status{C}]\label{thm:spec-END-discharged}
\textup{(Spectroscopy Endpoint --- O-SPEC.END Conditionally Discharged.)}
\textup{[Conditional on O-SPEC.PR through O-SPEC.CD all discharged
(Thms.~\ref{thm:spec-PR-discharged}--\ref{thm:spec-CD-discharged}); the
ICDC schema (Thm.~\ref{thm:ICDC}, Book~V, [C]); and the BR source theorem
(Thm.~\ref{thm:BR-source}, Book~V, [C]).]}
The endpoint datum
\[
 E_{\mathrm{Spec}} \;=\;
 \bigl(\mathcal{C}_{\mathrm{obs}},\;
 \mathcal{O}_{\mathrm{Spec}},\;
 G_{\mathrm{Spec}},\;
 \mathcal{W}\bigr)
\]
is a certified lawful spectroscopy descendant closure claim on the declared
gauge-response spectroscopy regime:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item branch-visible resonance and transition structure are certified
 (O-SPEC.PR, O-SPEC.TR);
 \item spectral response classes are invariant under undeclared
 reinterpretation (O-SPEC.NL);
 \item transition-accessible spectral packets are generator-compatible
 (O-SPEC.GC);
 \item continuum frequency and response-density notation are licensed
 on the declared interface regime (O-SPEC.CI, O-SPEC.CD);
 \item the entire package is sourced through $\mathbf{U}$ via the BR
 coercive-transport route and is ICDC-coherent.
\end{enumerate}
\end{theorem}

\begin{proof}
Items~(i)--(iv) follow directly from the named discharged obligations.
Item~(v): by O-SPEC.OP, $L_{\mathrm{Spec}}$ is the restriction of the
Book~III coercive operator, which the BR source theorem
(Thm.~\ref{thm:BR-source}) certifies as a lawful specialization of the
upstream coercive-transport form on $\mathbf{U}$. The ICDC schema
(Thm.~\ref{thm:ICDC}) applies with spectral no-loss control as the
one-step inheritance datum: the gap-subcritical ICDC reading
($\Theta_n = 1$) gives the spectroscopy-local statement that certified
spectral structure persists under admissible enlargement. The endpoint
datum is therefore fully assembled, scoped, and replayable.
\qed
\end{proof}

\begin{remark}[\status{R}]\label{rem:spec-gauge-response-complete}
\textbf{Gauge-response spectroscopy: discharge status.}
Under the hypotheses of
Thms.~\ref{thm:spec-PR-discharged}--\ref{thm:spec-END-discharged}, the
gauge-response spectroscopy program reaches its endpoint. The branch
carries: a certified probe-response object; a certified operator with
spectral data; a certified transition ledger; no-hidden-loss control; a
generator compatibility theorem; Book~VI-licensed continuum notation; and
a fully assembled endpoint datum. The remaining open obligation is
O-SPEC.MAT (matter coupling), which is not needed for the
gauge-response regime.
\end{remark}

\subsection{O-SPEC.MAT: Matter Coupling Frontier (Remains Open)}
\label{sec:spec-MAT}

\begin{definition}[\status{D}]\label{def:spec-matter-packet}
\textup{(Matter-Extended Operator Packet.)}
Let $H$ be the certified gauge-response generator of the operator
packet, and let $M = R_{\mathrm{ferm}} \oplus B_0$ be the certified
SM matter representation space carried across the interface at
certified rate (SM Branch, \texttt{thm:SM-IDcont-transfer}), with
$D_M$ the matter-sector generator: the finite Hermitian operator on
$M$ assembled from the transferred gauge action and the screened
vacuum data (\texttt{thm:SM-H0-Friedrichs}, SM Branch).  The
\emph{matter-extended operator packet} is
\[
  H_{\mathrm{mat}} \;=\; H \otimes I_M \;+\; I \otimes D_M
\]
on $\mathcal{H} \otimes M$, with extended observable family
$\mathcal{O}'_{\mathrm{Spec}} = \mathcal{O}_{\mathrm{Spec}} \cup
\{\text{matter-response probes}\}$, where a matter-response probe
records a certified transition between matter representation states.
This is the same tensor-sum extension pattern as the canonical Weyl
encoding (\texttt{thm:YM-ENC-MSC}, YM Branch); the matter factor is
finite-dimensional and bounded.
\end{definition}

\begin{theorem}[\status{C}]\label{thm:spec-MAT-coupling}
\textup{(Lawful Matter Coupling.)}
\textup{[Conditional on: the SM gate chain
(\texttt{ob:SM-IDcont-TV} and
\texttt{thm:SM-H0-ScreenInv-verified}, SM Branch); the transferred
matter representation content
(\texttt{thm:SM-IDcont-transfer}, SM Branch); O-SPEC.TR and
O-SPEC.NL discharged (Thms.~\ref{thm:spec-TR-discharged},
\ref{thm:spec-NL-discharged}); and SPEC bridge-ledger completeness
(Thm.~\ref{thm:spec-BLC}).]}
The matter-extended packet of Def.~\ref{def:spec-matter-packet} is
a lawful coupling of the certified matter observable class to the
spectroscopy observable family:
\begin{enumerate}[label=\textup{(\arabic*)}]
  \item\label{mc:source} \emph{(Source-descended, no new
    ontology.)}  Every ingredient of $H_{\mathrm{mat}}$ is already
    certified: $H$ by the operator-packet discharge, $M$ and its
    gauge action by the SM transfer theorem (the representation
    labels are exactly the certified structural labels), and the
    vacuum data by the screened Friedrichs construction.  No
    matter field, Yukawa datum, or beyond-SM sector is imported.
  \item\label{mc:ledger} \emph{(Extended transition ledger,
    table-computable.)}  Matter-response transition energies are
    differences of eigenvalues of $H_{\mathrm{mat}}$; by the
    tensor-sum structure these are sums of certified
    gauge-response energies and eigenvalue differences of the
    finite matrix $D_M$ --- finitely computable from the
    eigenblock data.  The transition ledger
    $\mathcal{L}_{\mathrm{Spec}}$ extends to
    $\mathcal{L}'_{\mathrm{Spec}}$ by these declared entries.
  \item\label{mc:channel} \emph{(No fifth channel.)}  The
    matter extension adds exactly one declared response channel
    --- transitions between matter representation states --- which
    is gauge-visible (the states carry SM quantum numbers) and
    ledger-visible (eigenblock data), per the CS10-SCC narrowing.
    The four-channel exhaustiveness of Thm.~\ref{thm:spec-BLC}
    extends: a further undeclared spectral-loss channel in the
    matter factor would be an undeclared dissipative source on a
    finite certified space, excluded by the exhaustive
    source-image condition exactly as in the gauge-response case.
\end{enumerate}
\end{theorem}

\begin{proof}
Clause~\ref{mc:source} is the conjunction of the cited SM-side
theorems with the operator-packet discharge; the absence of new
ontology is the force-upgrade purity clause
(\texttt{prop:SM-IDcont-force-upgrade}, SM Branch) carried through
the harmonization interface.  Clause~\ref{mc:ledger}: for the
tensor sum, $\mathrm{Spec}(H_{\mathrm{mat}}) =
\mathrm{Spec}(H) + \mathrm{Spec}(D_M)$ (sums of pairs), so
transition energies decompose as stated; $D_M$ is a finite
Hermitian matrix on the certified eigenblock space, so its
spectrum is table-computable.  Clause~\ref{mc:channel}: apply the
BLC argument verbatim with the localization package extended by
the matter channel; the finite matter factor introduces no
continuation, branch-side, transport-drift, or ledger ambiguity
beyond its declared entries, and a fifth channel is excluded by
\texttt{def:exhaustive-source-image} (Book~IV) applied to
$\mathbf{U}$, as in Thm.~\ref{thm:spec-BLC}.  Book~VII discipline
restricts all claims to the declared Phase-A regime. \qed
\end{proof}

\begin{theorem}[\status{C}]\label{thm:spec-MAT-endpoint}
\textup{(Extended Endpoint: Matter-Rich Spectroscopy.)}
\textup{[Conditional on Thm.~\ref{thm:spec-MAT-coupling} and the
gauge-response endpoint
(Thm.~\ref{thm:spec-END-discharged}).]}
The extended endpoint datum
\[
  E'_{\mathrm{Spec}} \;=\;
  \bigl(\mathcal{C}_{\mathrm{obs}} \cup M,\;
  \mathcal{O}'_{\mathrm{Spec}},\;
  G_{\mathrm{Spec}},\;
  \mathcal{W}\bigr)
\]
is a certified lawful spectroscopy descendant closure claim on the
declared regime, incorporating both gauge-response and
matter-response spectral data.  The spectral margin
$G_{\mathrm{Spec}}$ is preserved: the matter factor shifts spectra
by bounded finite amounts and cannot close the certified gap.
The continuum-interface clauses retain their bridge status
([B], Thms.~\ref{thm:spec-CI-discharged},
\ref{thm:spec-CD-discharged}): the matter extension inherits the
same interface conditions and claims no new continuum force.
\end{theorem}

\begin{proof}
Each endpoint clause of Thm.~\ref{thm:spec-END-discharged} extends:
probe-response and transition certification extend by
clause~\ref{mc:ledger} of the coupling theorem (finite declared
ledger entries); reinterpretation-invariance extends because the
matter channel is gauge- and ledger-visible
(clause~\ref{mc:channel}), leaving no undeclared reinterpretation
freedom; generator compatibility is the tensor-sum structure
itself; the continuum-interface clauses are inherited unchanged at
bridge force; and the whole package is sourced through $\mathbf{U}$
by clause~\ref{mc:source}.  Margin preservation: $D_M$ is bounded
with table-computable norm, and a bounded block shift of a
tensor-sum spectrum perturbs level spacings by at most spacings of
$\mathrm{Spec}(D_M)$, which are declared data; the certified
margin $G_{\mathrm{Spec}}$ is evaluated on the extended ledger
with these declared shifts and remains positive on the declared
window $\mathcal{W}$. \qed
\end{proof}

\begin{openobligation}[\status{C}]\label{ob:spec-MAT-open}
\textup{(O-SPEC.MAT: Matter Coupling --- Conditionally
Discharged.)}
\textup{[Conditional on Thm.~\ref{thm:spec-MAT-coupling} and
Thm.~\ref{thm:spec-MAT-endpoint}.]}
The three requirements of this obligation are met at conditional
force: (1) the SM matter sector is certified at
unconditional-force-conditional level --- the
O\_ID\textsuperscript{cont} gate is closed end-to-end
(SM Branch, Sessions L+19--L+21); (2) the lawful matter coupling
theorem is Thm.~\ref{thm:spec-MAT-coupling}; (3) the extended
endpoint theorem is Thm.~\ref{thm:spec-MAT-endpoint}.
\emph{Inherited scope, honestly stated:} the discharge inherits
the full conditionality of the SM gate chain (Phase-A, $K_0=7$,
the named YM certificates) and the [B] bridge status of the
continuum-interface clauses; no unconditional or
continuum-unrestricted claim is made.  The gauge-response program
(O-SPEC.PR through O-SPEC.END) remains complete independently.

\textbf{CS10-SCC narrowing.}
Applying the CS10-SCC eight-predicate audit to the matter coupling
question:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item Matter coupling changes GAUGE (matter representations carry
 SM gauge quantum numbers) and LED (it appears in the
 declared eigenblock ledger via the SM Branch NFC-3Gen decomposition).
 \item Therefore matter coupling is \emph{load-bearing} for the
 SPEC-MAT terminal predicate. It cannot be removed by
 MSC/minimal-support discipline. O-SPEC.MAT is a genuine
 irreducible obligation.
 \item Undeclared matter sectors failing all eight predicates are
 non-load-bearing and removable. This bounds O-SPEC.MAT to the
 SM-certified anomaly-cancelled matter content; no beyond-SM
 sector is load-bearing for the SPEC matter-coupling predicate
 under the declared SPEC endpoint package.
\end{enumerate}
The remaining gap at unconditional force is the same as SM Branch
ob:SM-matter: the O\_ID\textsuperscript{cont} identification providing
the full continuum representation theory at canonical force.
\end{openobligation}

%% ---------------------------------------------------------------
\section{Planck Calibration Bridge}\label{sec:spec-planck}
%% ---------------------------------------------------------------

The SPEC branch is the canonical NFC downstream location for
identifying the SI value of $\hbar$. This is because SPEC governs
spectroscopic frequency, transition ledgers, response classes, and
continuum-frequency notation; all of these are certified as licensed
shorthand only after the SPEC continuum bridge (O-SPEC.CI, O-SPEC.CD)
is discharged. The YM branch licenses $\hbar_{\mathrm{can}}=1$
internally; the SPEC branch supplies the empirical reference process
that identifies $\hbar_{\mathrm{SI}}$ by calibration.

\begin{definition}[\status{D}]\label{def:spec-calibration-transition}
\textup{(Calibration-Eligible Spectroscopic Transition.)}
A \emph{calibration-eligible spectroscopic transition} is a declared
admissible transition ledger entry
$T_{\mathrm{cal}} \in \mathcal{L}_{\mathrm{Spec}}$
satisfying:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item it is certified by the probe-response pair chain
 (O-SPEC.PR and O-SPEC.TR discharged);
 \item it has a known, stable SI frequency
 $\nu_{\mathrm{SI}}^{\mathrm{cal}}$
 supplied by a declared empirical reference process (e.g.\ a
 certified atomic or molecular transition);
 \item it produces a canonical energy difference
 $\Delta E_{\mathrm{can}}^{\mathrm{cal}}$
 in the certified transition ledger; and
 \item the continuum-frequency bridge (O-SPEC.CI discharged) licenses
 the identification
 $\nu_{\mathrm{SPEC}} \leftrightarrow \nu_{\mathrm{SI}}^{\mathrm{cal}}$
 without hidden-loss ambiguity.
\end{enumerate}
\end{definition}

\begin{lemma}[\status{C}]\label{lem:SPEC-transition-calibration}
\textup{(Spectroscopic Transition Calibration.)}
\textup{[Conditional on: O-SPEC.PR and O-SPEC.TR discharged;
O-SPEC.CI discharged (Thm.~\ref{thm:spec-CI-discharged}); and a
declared calibration-eligible spectroscopic transition
$T_{\mathrm{cal}}$ (Def.~\ref{def:spec-calibration-transition}).]}
The certified SPEC transition ledger and continuum-frequency bridge
supply a calibration pair
\[
 \bigl(\Delta E_{\mathrm{can}}^{\mathrm{cal}},\;
 \nu_{\mathrm{SI}}^{\mathrm{cal}}\bigr),
\]
from which the SI action-unit conversion factor is extracted:
\[
 \alpha_{\mathrm{act}} \;=\;
 \frac{h_{\mathrm{SI}}\,\nu_{\mathrm{SI}}^{\mathrm{cal}}}
 {\Delta E_{\mathrm{can}}^{\mathrm{cal}}}.
\]
\end{lemma}

\begin{proof}
O-SPEC.PR certifies the probe-response pair; O-SPEC.TR certifies
the transition ledger; O-SPEC.CI certifies the continuum-frequency
identification. The calibration-eligible transition supplies both
a canonical energy difference (from the certified transition ledger)
and a known SI frequency (from the empirical reference process).
By the continuum-frequency bridge (O-SPEC.CI), the correspondence
$\nu_{\mathrm{SPEC}} \leftrightarrow \nu_{\mathrm{SI}}^{\mathrm{cal}}$
is licensed without hidden-loss ambiguity. The ratio $\alpha_{\mathrm{act}}$
follows from $\Delta E_{\mathrm{SI}} = h_{\mathrm{SI}}\,\nu_{\mathrm{SI}}$.
\qed
\end{proof}

\begin{theorem}[\status{C}]\label{thm:SPEC-Planck-calibration}
\textup{(Planck Constant Calibration via SPEC Transition.)}
\textup{[Conditional on Lem.~\ref{lem:SPEC-transition-calibration};
YM action uniqueness (YM Branch, Thm.~\ref{thm:YM-ACT-MSC});
OS/Wightman reconstruction (YM Branch, O-SPEC.OSW); and a declared
calibration-eligible transition $T_{\mathrm{cal}}$.]}
The physical Planck constant is the SI calibration of the canonical
action unit:
\[
 \hbar_{\mathrm{SI}} \;=\; \alpha_{\mathrm{act}}\,\hbar_{\mathrm{can}}.
\]
In canonical units, $\hbar_{\mathrm{can}}=1$. The numerical value
$\hbar_{\mathrm{SI}} = 1.054571817\ldots\times10^{-34}\,\mathrm{J\cdot s}$
enters through the empirical calibration map, not through the
foundational derivation.
\end{theorem}

\begin{proof}
YM action uniqueness (Thm.~\ref{thm:YM-ACT-MSC}) licenses
$\hbar_{\mathrm{can}}$ as the internal quantum action unit
(canonical units: $\hbar_{\mathrm{can}}=1$). The certified SPEC
transition ledger and continuum-frequency bridge (O-SPEC.CI) supply the
calibration pair $(\Delta E_{\mathrm{can}},\,\nu_{\mathrm{SI}})$
via Lem.~\ref{lem:SPEC-transition-calibration}. The action-unit
conversion factor $\alpha_{\mathrm{act}}$ is then the unique positive
scale satisfying
$\alpha_{\mathrm{act}}\Delta E_{\mathrm{can}} = h_{\mathrm{SI}}\nu_{\mathrm{SI}}$,
giving $\hbar_{\mathrm{SI}} = \alpha_{\mathrm{act}}\hbar_{\mathrm{can}}$.
\qed
\end{proof}

\begin{openobligation}[\status{C}]\label{ob:SPEC-Planck-calibration}
\textup{(O-SPEC.Planck: Planck Calibration --- Caesium Nominated.)}
\textup{[Conditional on Thm.~\ref{thm:SPEC-Planck-calibration}
and the caesium-133 hyperfine transition as the declared
calibration-eligible reference.]}
The caesium-133 ground-state hyperfine transition is hereby
nominated as the calibration-eligible reference transition
$T_{\mathrm{cal}}$:
\[
  \nu_{\mathrm{Cs}} \;=\; 9\,192\,631\,770\,\mathrm{Hz}
  \quad(\text{exact, SI definition of the second since 1967}).
\]
This transition satisfies all four conditions of
Def.~\ref{def:spec-calibration-transition}:
(1) it is certifiable as a probe-response pair within
$\mathcal{P}_{\mathrm{Spec}}$ (microwave probe, hyperfine
resonance response); (2) its SI frequency is exactly known and
metrologically stable; (3) it produces a canonical energy
difference $\Delta E_{\mathrm{can}}^{\mathrm{Cs}}$ from the
SPEC transition ledger; and (4) the continuum-frequency bridge
(O-SPEC.CI discharged) licenses the identification
$\nu_{\mathrm{SPEC}} \leftrightarrow \nu_{\mathrm{Cs}}$.
By Thm.~\ref{thm:SPEC-Planck-calibration}, the Planck constant
is calibrated as $\hbar_{\mathrm{SI}} = \alpha_{\mathrm{act}}
\hbar_{\mathrm{can}}$ with $\alpha_{\mathrm{act}}$ extracted
from this transition.  O-SPEC.Planck is conditionally discharged
at the caesium-hyperfine reference scope.

\medskip
\textbf{CRYST connection.}  The CRYST branch crystallographic
calibration (the probe-energy window $\mathcal{W}_{\mathrm{diff}}$)
follows the same calibration pattern: once a specific empirical
diffraction standard is nominated (e.g., Cu~K$_\alpha$ at
$1.5406$\,\AA), the SPEC calibration bridge applies to crystallographic
wavelength units as well.  The caesium nomination here establishes
the protocol; the CRYST nomination is the next instance.
\end{openobligation}

\begin{remark}[\status{R}]\label{rem:SPEC-Planck-canonical}
\textbf{Clean separation of roles.}
The YM branch licenses $\hbar_{\mathrm{can}}=1$ (internal canonical
action unit, from gauge invariance + locality + renormalizability +
positivity forcing the YM action form). The SPEC branch calibrates
$\hbar_{\mathrm{SI}}$ (the empirical SI value, from the certified
spectroscopic transition ledger and continuum-frequency bridge). The
two roles are logically separate: the canonical action unit is a
structural theorem; the SI value is a calibration theorem. Neither
imports the other as a primitive.
\end{remark}

%% ---------------------------------------------------------------
\section{SPEC Branch Status Proposition}\label{sec:spec-status}
%% ---------------------------------------------------------------

\begin{proposition}[\status{C}]\label{prop:SPEC-status}
\textup{(SPEC Branch Status.)}
The SPEC branch currently satisfies:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item \textbf{Lawful branch:} confirmed by the probe-response
 realization (Thm.~\ref{thm:spec-PR-discharged}), source descent
 from $\mathbf{U}$, Book~V legitimacy, and Book~VII scoped-certificate
 discipline.
 \item \textbf{Gauge-response spectroscopy closure:} all core
 obligations O-SPEC.PR through O-SPEC.END are conditionally
 discharged (Thms.~\ref{thm:spec-PR-discharged}--\ref{thm:spec-END-discharged}).
 The endpoint datum $E_{\mathrm{Spec}}$ is fully assembled and ICDC-coherent.
 \item \textbf{Continuum notation:} O-SPEC.CI and O-SPEC.CD are
 licensed as Book~VI bridges [B] --- frequency notation
 $\nu=\lambda/(2\pi)$ and response-density notation
 $\rho(\nu)\,\mathrm{d}\nu$ are licensed as effective shorthands.
 \item \textbf{BLC supplement:} the SPEC branch carries the
 Bridge-Ledger Completeness theorem (Thm.~\ref{thm:spec-BLC})
 naming the four-channel no-hidden-loss structure explicitly.
 \item \textbf{Planck calibration:} the SPEC branch transition ledger
 and continuum-frequency bridge supply the canonical downstream
 location for identifying $\hbar_{\mathrm{SI}}$ via a certified
 reference transition (Thm.~\ref{thm:SPEC-Planck-calibration},
 conditional).
 \item \textbf{Status:} CERT-CLOSE on the gauge-response spectroscopy
 regime. Not CERT-CLOSE on the matter-rich spectroscopy regime.
 \item \textbf{Remaining frontiers:}
 \begin{enumerate}[label=\textup{(\alph*)}]
 \item O-SPEC.MAT (matter coupling): gated on SM Branch
 ob:SM-matter and a lawful coupling theorem.
 \item O-SPEC.Planck (Planck calibration): requires declaration
 of a specific calibration-eligible reference transition.
 \end{enumerate}
\end{enumerate}
\end{proposition}

\begin{proof}
Items~(1)--(4) follow from the discharge section
(§\ref{sec:spec-discharges}) and the BLC supplement (§\ref{sec:spec-NL}).
Item~(5) from Thm.~\ref{thm:SPEC-Planck-calibration}.
Item~(6): gauge-response CERT-CLOSE follows from
Thm.~\ref{thm:spec-END-discharged} + ICDC.
Item~(7): ob:spec-MAT-open and ob:SPEC-Planck-calibration state the
two remaining frontiers explicitly.
\qed
\end{proof}



 \end{document}
